---
title: "RUG June 2018"
author: "Gwendolyn"
date: "6/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

Professor of Computer Science at the UofU:  Miriah Meyer from the Visualization Design Lab, applied visualization research
Book: Making Data Visual 

MizBee tool to support genome comparison data. It is like a donut chart with lines going to and from each other. 

Visualization is a design process. 

User centered design: understand -> ideate -> make -> deploy, evaluate at every step

Data Counseling:
interviews, exploratory data analysis, and rapid prototyping

Thought: prototype rather than drafts or wireframes

Proxy: a partial and imperfect representation of the thing the analyst cares about

action: thing you want to do
object: items you want to take action on
measure: value you are interested in for the objects

Translate fuzzy task into something you can do with your data. 

Poemage v 0.1 

What does this mean for visualization design? 
-If we aren't using visualizations to find the accurate answer, how does that change how we design visualizations? 

www.cs.utah.edu/~miriah
miriah@cs.utah.edu

Book that combines things and has a ranked order list of research based encodings for creating visualizations.
Multiple linked views--data is complex, you can't shove everything into one visualization. Don't make any one graph crazy complex. 

Grammar of graphics, d3, R, Matlab, etc









```{r}

```



```{r pressure, echo=FALSE}
plot(pressure)
```


